Computer Science House Constitution

### 2016-01-26 articles.tex
typo

>>>>

\asection{Maintainers}

\asubsection{Maintainer Qualifications}
Maintainers must have Active or Alumni in good standing status.

\asubsection{Maintainer Expectations}
Maintainers are expected to:
\begin{itemize}
    \item Review changes to the Constitution for grammar, spelling, and internal consistency.
    \item Participate in discussion of proposals.
    \item Facilitate the creation of new changes to the Constitution by other members.
    \item Be knowledgeable about the Constitution. 
\end{itemize}
Failure to adequately meet any of these expectations is grounds for revocation of maintainer status.

\asubsection{Maintainer Resignations}
Maintainers may resign at any time by notifying the current eboard and maintainer group.

\asubsection{Maintainer Term}
Maintainer status lasts until it is resigned, or revoked by Executive Board vote.

\asubsection{Maintainer Selection}
Any member may nominate a qualified member for Maintainer status to the Executive Board for consideration. The Exective Board may choose to approve or reject the nomination by Simple Majority vote.
